Title

### 2021-05-25 paper/main.tex
Added more 'previous simulations' references

First synthesized in 2004 \cite{Novoselov_2004}, graphene has since
experienced an explosive growth in interest \cite{Randviir_2014}.
For pristine graphene, it's interactions with other particles are
mainly due to Van der Waals forces and $\pi-\pi$ stacking. \cite{Zuo_2012}
As pristine graphene is chemically inert \cite{Eftekhari_2017} a
classical description of it is expected to suffice in simulations.
Multiple studies on the interactions between proteins and graphene
have been published (TODO citation).

>>>>

First synthesized in 2004 \cite{Novoselov_2004}, graphene has since
experienced an explosive growth in interest \cite{Randviir_2014}.  For
pristine graphene, it's interactions with other particles are mainly
due to Van der Waals forces and $\pi-\pi$ stacking. \cite{Zuo_2012} As
pristine graphene is chemically inert \cite{Eftekhari_2017} a
classical description of it is expected to suffice in simulations.
Multiple molecular dynamics studies on the interactions between
proteins and carbon based nanoparticles (CBNs) --such as graphene--
have been published \cite{Zheng_2003, Ge_2011, Zuo_2012, Chong_2015,
  Duan_2015, Shityakov_2015, Al_Qattan_2018,Puigpelat_2019,
  Gonz_lez_Durruthy_2020, Li_2020}
